Selective stock enhancement undermines community stability

### 2022-01-23 rmd/supporting_info.Rmd
Update supporting_info.Rmd

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE)
options(knitr.kable.NA = '')

@@

```{=tex}
\newpage
\pagenumbering{arabic}
```
# Tables

@@

j <- 5

## load regression tables
source(here::here("code/table_reg.R"))

@@

>>>>

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
options(knitr.kable.NA = '')

@@

```{=tex}
\newpage
\pagenumbering{arabic}
```

# Tables

@@

## load regression tables
source(here::here("code/table_reg.R"))
j <- 5

@@

```{r figure_main}

## load figures
source(here::here("code/figure_suppl.R"))

j <- 0
figure_sim_chunk <- knit_chunk <- NULL

for(i in seq_len(nrow(df_param))) {

  knit_chunk <- paste0("## Figure S", i + j,
                       " Theoretical prediction (",
                       "$r_1$ = `r df_param$r1[",i,"]`, ",
                       "$\\sigma_{env}$ = `r df_param$sd_env[",i,"]`, ",
                       "$K$ = `r df_param$k[",i,"]`) \n",

                       "\n```{r figure_s", i + j,", fig.width = 9.5, fig.height = 8}
                       \n\n
                       list_g[[",i,"]]
                       \n\n
                       ```\n",

                       "Theoretical predictions for the stocking effect on community dynamics. Rows represent different response varaibles, and columns show distinct simulation scenarios with different strength of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$). Other parameters used in this analysis is the following: ",
                       "intrinsic growth rate of enhanced species $r_1$ = `r df_param$r1[",i,"]`; ",
                        "environmental variability $\\sigma_{env}$ = `r df_param$sd_env[",i,"]`; ",
                        "carrying capacity $K$ = `r df_param$k[",i,"]`.",
                        "\n\\pagebreak\n")

  figure_sim_chunk <- c(figure_sim_chunk, knit_chunk)

`r paste(knit(text = figure_sim_chunk), collapse = '\n')`
